|

### 2023-01-29 paper.Rmd
Sun Jan 29 10:00:05 CET 2023: update-remote.sh

```{r altStrategies-Fitness, echo=FALSE, fig.cap="Best Fitness over 30 Generations - Alternative Pre-Trategies - Airfoil", out.width="80%"}
knitr::include_graphics("./img/PT_Strategies_airfoil_2hl_150hn_fullRun/median_fitness_byGens.png")
```

@@

```{r altStrategies-FitnessDistr, echo=FALSE, fig.cap="Best Fitness after 30 Generations - Alternative Pre-Trategies - Airfoil", out.width="80%"}
knitr::include_graphics("./img/PT_Strategies_airfoil_2hl_150hn_fullRun/final_fit_boxplot(test_only).png")
```

>>>>

```{r altStrategies-Fitness, echo=FALSE, fig.cap="Best Fitness over 30 Generations - Alternative Pre-Strategies - Airfoil", out.width="80%"}
knitr::include_graphics("./img/PT_Strategies_airfoil_2hl_150hn_fullRun/median_fitness_byGens.png")
```

@@

```{r altStrategies-FitnessDistr, echo=FALSE, fig.cap="Best Fitness on Test Set after 30 Generations - Alternative Pre-Trategies - Airfoil", out.width="80%"}
knitr::include_graphics("./img/PT_Strategies_airfoil_2hl_150hn_fullRun/final_fit_boxplot(test_only).png")
```

### 2023-01-29 paper.tex
Sun Jan 29 10:00:05 CET 2023: update-remote.sh

Master Thesis

@@

\caption{Best Fitness over 30 Generations - Alternative Pre-Trategies - Airfoil}\label{fig:altStrategies-Fitness}
\end{figure}

@@

\caption{Best Fitness after 30 Generations - Alternative Pre-Trategies - Airfoil}\label{fig:altStrategies-FitnessDistr}
\end{figure}

>>>>

@@

\caption{Best Fitness over 30 Generations - Alternative Pre-Strategies - Airfoil}\label{fig:altStrategies-Fitness}
\end{figure}

@@

\caption{Best Fitness on Test Set after 30 Generations - Alternative Pre-Trategies - Airfoil}\label{fig:altStrategies-FitnessDistr}
\end{figure}
